A Comprehensive Dataset of U.S. Federal Laws, 1789-2022

### 2023-09-27 draft/v1.tex
final submission changes
Updates from Overleaf

All code used to create the dataset from original sources, is available through a Github repository made public upon publication. Also included in the repository are code and data used to validate the dataset as well as generate the figure. \footnote{\url{https://github.com/libgober/database_of_laws}}

@@

% The corresponding author is responsible for providing a \href{https://www.nature.com/sdata/policies/editorial-and-publishing-policies#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

>>>>

All code used to create the dataset from original sources, is available through a Github repository made public upon publication. Also included in the repository are code and data used to validate the dataset as well as generate the figure. \footnote{\url{https://github.com/libgober/database_of_laws}}. Versions of these files used at time of submission to \textit{Scientific Data} are available in the OSF repository.

@@

The author declares that he has no competing interests related to the research, authorship, or publication of this manuscript, and no conflicts of interest, financial or otherwise, exist.
% The corresponding author is responsible for providing a \href{https://www.nature.com/sdata/policies/editorial-and-publishing-policies#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.
